---
title: "Classic Inference"
author: "Stats for data science"
date: "USCOTS May 14, 2019"
output: rmdformats::material
---

```{r setup_classic, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(SDSdata)
library(mosaic)
library(mosaicCore)
```

# CIs and p-values

Much of the inference part of conventional intro stats is about computing confidence intervals and p-values in a variety of settings:

- difference of means
- difference of proportions
- slope of regression line

Formulas from Triola

# No statistics were harmed in the filming of this documentary

In the following, spread is measured using the length of the 85% summary interval. 

You can still do all this by using the standard deviation instead.

# The procedure

1. Plot out data, draw in model.
2. From data and model, find R and sample size n. The picture will tell you R.
3. Measure effect size, e.g. difference in means or slope of regression line. Call it $\Delta$.
4. Calculate $F = n-2 \frac{R^2}{1-R^2}$.
5. 95% confidence interval on $\Delta$ is $\Delta \pm \sqrt{4/F}$.
6. "Significance", but let's call it ... ?
    - $F = 4$ -- one star (corresponds to about 0.05)
    - $F = 7$ -- two stars (corresponds to about 0.01)
    - $F = 12$ -- three stars (corresponds to about 0.001)
    
# The F table

```{r echo = FALSE}
Ftable <- data.frame(df = 3:100) %>%
  mutate(five = qf(.95, 1, df), 
         one = qf(.99, 1,  df), 
         oh_one = qf(.999, 1, df))
gf_ribbon(0 + five ~ df, data = Ftable, fill = "red", alpha = 0.2) %>%
  gf_ribbon(five + pmin(15, one) ~ df, fill = rgb(.8, .49, .19, .7)) %>%
  gf_ribbon(pmin(15,one) + pmin(15,oh_one) ~ df, fill  = rgb(.52, .59, .6, .7))  %>%
  gf_ribbon(pmin(15,oh_one) + 15 ~ df, fill  = rgb(.83, .69, .22, 0.7)) %>%
  gf_lims(y = c(0, 15), x = c(1, 100)) %>%
  gf_labs(title = "Olympic shading for significance", y = "F", x = "n - 1") %>%
  gf_theme(theme_minimal())
```

# Difference of means


```{r echo = FALSE}
This_data <- KidsFeet %>% left_join(df_stats(width ~ sex, data = KidsFeet, mean))
P <- gf_jitter(width ~ sex, data = This_data, width = 0.1) %>%
  gf_errorbar(mean_width + mean_width ~ sex, data = This_data, width = .25) %>%
  gf_jitter(width ~ 1.7, width = .05, height = 0, alpha = .25) %>%
  gf_jitter(mean_width~ 1.3, width = 0.1, height = 0, alpha = 0.25, color = "blue")
P %>% 
  gf_labs(y = "Foot width (cm)", title = "Raw and model values")
```

```{r echo = FALSE}
Interval1 <- df_stats(mean_width ~ 1, data = This_data, mean = mean, sd = sd) %>% mutate(lower = mean -  0.8 * sd, upper = mean + 0.8 *sd)
Interval2 <- df_stats(width ~ 1, data = This_data, coverage(0.85))
P %>%
  gf_errorbar(lower + upper ~ 1.3, data = Interval1, color = "blue",
              width = 0.2) %>%
  gf_errorbar(lower + upper ~ 1.7, data = Interval2, width = 0.2) %>%
  gf_labs(y = "Foot width (cm)", title = "Raw interval and model-value interval")
```

The ratio of the intervals is $R \approx 0.25$ (and $n = 39)$.

- **Difference** between the means: read it off the graph: ∆.

- **CI** on difference between means: ∆ (1 ± $\sqrt{\frac{1-R^2}{n-2}})$

- "**Significance**" is $(n-2) \frac{R^2}{1-R^2}$
    - One star when 4, two stars when 7, three stars when 12.

# Regression slope

```{r echo = FALSE}
This_data <- KidsFeet %>% 
  mutate(mod_val = predict(lm(width ~ length, data = This_data)))
P <- gf_jitter(width ~ length, data = This_data, height = 0.0, width = 0) %>%
  gf_lm() %>%
  gf_jitter(width ~ 29, width = .1, height = 0,  alpha = .25) %>%
  gf_jitter(mod_val ~ 28, width = .1, height = 0, alpha = 0.25, color = "blue") %>%
  gf_point(mod_val~ length, width = 0.1, height = 0, alpha = 0.25, color = "blue")
P %>% 
  gf_labs(y = "Foot width (cm)", title = "Raw and model values")
```



```{r echo = FALSE}
Interval1 <- df_stats(mod_val ~ 1, data = This_data, coverage(.85))
Interval2 <- df_stats(width ~ 1, data = This_data, coverage(0.85))
Interval3 <- df_stats(length ~ 1, data = This_data, coverage(0.85)) %>%
  mutate(y = 8)
P %>%
  gf_errorbarh(y ~ lower + upper, data = Interval3, inherit = FALSE,
               width = 0.2) %>%
  gf_errorbar(lower + upper ~ 28, data = Interval1, color = "blue",
              width = 0.2) %>%
  gf_errorbar(lower + upper ~ 29, data = Interval2, width = 0.2) %>%
  gf_labs(y = "Foot width (cm)", title = "Raw interval and model-value interval")
```


The ratio of the vertical intervals is about $R \approx 0.65$ (and $n = 39$).

- **Slope** is ratio of rise interval over run interval. Call it ∆.

- **CI** on slope: ∆ (1 ± $\sqrt{\frac{1-R^2}{n-2}})$

- "**Significance**" is $F = (n-2)\frac{R^2}{1-R^2}$
    - One star when 4, two stars when 7, three stars when 12.
    
# Difference in proportions

Fill in an example, say, domhand versus sex

# Slope of proportion


Fill in an example, say sex versus width.

# Multiple regression



