---
title: "Mean and standard deviation"
author: "Stats for data science"
date: "USCOTS May 14, 2019"
output: rmdformats::material
---

```{r setup_mean, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(SDSdata)
library(mosaic)
```


# Spread without mean

First proposal: Focus on prediction, not "typical." 85% summary interval.

How to define "spread" without a mean to refer it to? 

- Could use length of the interval. 

Second proposal: Define spread as the average difference between pairs of individuals.

Formulas: 

$$D_2 = \sqrt{\frac{1}{n} \frac{1}{n-1} \sum_{i=1}^n \sum_{j=1}^n (x_i - x_j)^2}$$

... or ...

$$D_1 = \frac{1}{n} \frac{1}{n-1} \sum_{i=1}^n \sum_{j=1}^n |x_i - x_j|$$

For fun, let's see what these are for a standard normal distribution:

```{r}
n <- 1000
x <- rnorm(n)
vals <- outer(x, x, FUN = function(x, y) {abs(x - y)})
sum(vals[]) / (n * (n-1))
vals2 <- outer(x, x, FUN = function(x, y) {(x - y)^2})
sqrt(sum(vals2[]) / (n * (n-1)))
```

For a normal distribution, 

* $D_2$ is $\sqrt{2} \times$ standard deviation

* $D_1$ is 20% smaller. 

* Either can be used in what follows.

**More fun**: The $n-1$ term, obscure in the standard deviation, arises naturally here. In summing the $n^2$ terms, there will be $n$ of them that are $x_i - x_i$ and so must always be exactly zero.

# The 85% summary interval

The length of the 85% summary interval is $2 D_2$.


