---
title: "A Modest Proposal"
author: "Stats for data science"
date: "USCOTS May 14, 2019"
output: rmdformats::material
---

# Imagine Intro Stat 

Imagine there's no *center*    
- It's easy if you try.    
- No Null below us    
- Models explaining why    

Imagine deviation     
- Cast away for good (ah ah ah)      

Imagine diverse values      
- The math not hard to do      
- Difference not deviation      
- And forget error, too      

Imagine all the models      
- Living life in peace      

You can call that data science     
- But I'm not the only one      
- I hope someday you'll join us        
- And statistics will have won       

Imagine there's no normal       
- I wonder if you can      
- No need for spread or center        
- Just predict what you can        

Imagine all the data      
- Training models galore       

You can call that data science         
- But I'm not the only one         
- I hope someday you'll join us        
- And statistics will have won         


# Re-imagining intro inference

Why we might want to do this ....

```{r echo = FALSE, child = "prediction-not-typical.Rmd"}
```

```{r echo = FALSE, child = "mean-and-deviation.Rmd"}
```

```{r echo = FALSE, child = "classical-inference.Rmd"}
```
